### 2016-01-26 Manuscript/BiologyLetters/Table_results.tex
Changed to table without character threshold

% Sun Jun 21 15:26:40 2015

@@

\caption{Number of taxa with available cladistic data for mammalian orders at three taxonomic levels. The left vertical bar represents low coverage (\textless 25\%); the right vertical bar represents high coverage (\textgreater 75\%). Negative Net Relatedness Index (NRI) and Nearest Taxon Index (NTI) values indicate phylogenetic overdispersion; positive values indicate phylogenetic clustering. Significant NRI or NTI values are in bold. *p \textless 0.05; **p \textless 0.01; ***p \textless 0.001.} \\ 

@@

  \textbf{Afrosoricida} & \textbf{species} & \textbf{23/42} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar3.pdf} & \textbf{1.89*} & 1.19 \\ 
  Carnivora & family & 11/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar4.pdf} & 0.43 & 1.68 \\ 
  \textbf{Carnivora} & \textbf{genus} & \textbf{30/125} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar5.pdf} & \textbf{4.14**} & \textbf{1.81*} \\ 
  \textbf{Carnivora} & \textbf{species} & \textbf{42/283} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar6.pdf} & \textbf{18.64**} & \textbf{3.02**} \\ 

@@

  \textbf{Cetartiodactyla} & \textbf{genus} & \textbf{77/128} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar8.pdf} & 0.87 & \textbf{1.77*} \\ 
  \textbf{Cetartiodactyla} & \textbf{species} & \textbf{129/310} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar9.pdf} & \textbf{2.72*} & 0.04 \\ 
  Chiroptera & family & 13/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar10.pdf} & 0.55 & 0.63 \\ 
  \textbf{Chiroptera} & \textbf{genus} & \textbf{85/202} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar11.pdf} & \textbf{16.91**} & \textbf{2.85**} \\ 
  \textbf{Chiroptera} & \textbf{species} & \textbf{165/1053} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar12.pdf} & \textbf{14.55**} & \textbf{3.44**} \\ 

@@

  Cingulata & genus & 8/9 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar14.pdf} & 1.49 & -1.63 \\ 
  Cingulata & species & 6/29 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar15.pdf} & 1.43 & 0.36 \\ 

@@

  Dasyuromorphia & genus & 7/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar17.pdf} & -1 & -1.45 \\ 
  Dasyuromorphia & species & 8/64 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar18.pdf} & -1.15 & -0.62 \\ 

@@

  Didelphimorphia & species & 40/84 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar24.pdf} & -0.94 & 0.36 \\ 
  Diprotodontia & family & 9/11 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar25.pdf} & -0.8 & 0.56 \\ 
  Diprotodontia & genus & 20/38 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar26.pdf} & -1.36 & -0.73 \\ 
  Diprotodontia & species & 16/126 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar27.pdf} & -2.29 & -1.55 \\ 

@@

  Erinaceomorpha & species & 21/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar30.pdf} & -1.1 & -0.3 \\ 

@@

  Lagomorpha & family & 1/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar34.pdf} &   &   \\ 
  Lagomorpha & genus & 1/12 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar35.pdf} &   &   \\ 
  Lagomorpha & species & 1/86 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar36.pdf} &   &   \\ 

@@

  Macroscelidea & species & 5/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar39.pdf} & -0.98 & -1.38 \\ 

@@

  Monotremata & genus & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar44.pdf} & -0.71 & -0.71 \\ 
  Monotremata & species & 2/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar45.pdf} & -1.01 & -1.03 \\ 

@@

  Paucituberculata & genus & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar50.pdf} & 0 & 0 \\ 
  Paucituberculata & species & 2/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar51.pdf} & -0.64 & -0.65 \\ 

@@

  Peramelemorphia & species & 16/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar54.pdf} & -0.09 & 1 \\ 

@@

  Perissodactyla & species & 7/16 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar57.pdf} & 0.62 & -2.5 \\ 

@@

  \textbf{Pholidota} & \textbf{species} & \textbf{3/8} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar60.pdf} & \textbf{2.64*} & \textbf{2.23*} \\ 
  Pilosa & family & 3/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar61.pdf} & 0.94 & 0.93 \\ 
  Pilosa & genus & 3/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar62.pdf} & -0.36 & -0.31 \\ 
  Pilosa & species & 3/29 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar63.pdf} & 0.33 & 0.79 \\ 

@@

  Primates & genus & 48/68 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar65.pdf} & -0.41 & -1.4 \\ 
  Primates & species & 56/351 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar66.pdf} & -1.6 & -2.04 \\ 

@@

  Proboscidea & genus & 1/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar68.pdf} &   &   \\ 
  Proboscidea & species & 1/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar69.pdf} &   &   \\ 
  Rodentia & family & 11/32 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar70.pdf} & -0.46 & -1.91 \\ 
  Rodentia & genus & 21/450 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar71.pdf} & -2.11 & 0.3 \\ 
  Rodentia & species & 15/2094 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar72.pdf} & -1.65 & -2.55 \\ 

@@

  Scandentia & genus & 2/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar74.pdf} & -0.77 & -0.76 \\ 
  Scandentia & species & 2/20 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar75.pdf} & -1.79 & -1.99 \\ 

@@

  Soricomorpha & family & 3/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar79.pdf} & -0.93 & -0.92 \\ 
  \textbf{Soricomorpha} & \textbf{genus} & \textbf{19/43} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar80.pdf} & \textbf{6.98**} & \textbf{2.49*} \\ 
  \textbf{Soricomorpha} & \textbf{species} & \textbf{19/392} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar81.pdf} & \textbf{13.19**} & \textbf{3.89**} \\ 

>>>>

% Sat Jun 20 17:19:07 2015

@@

\caption{Number of taxa with available cladistic data for mammalian orders at three taxonomic levels (without any character threshold; results from the 286 matrices). The coverage represents the proportion of taxa with available morphological data. The left vertical bar represents 25\% of available data (``low'' coverage if \textless 25\%); The right vertical bar represents 75\% of available data (``high'' coverage if \textgreater 75\%). When the Net Relatedness Index (NRI) and the Nearest Taxon Index (NTI) are negative, taxa are more phylogenetically dispersed than expected by chance; when NRI or NTI are positive, taxa are more phylogenetically clustered by expected by chance. Significant NRI or NTI are highlighted in bold. *p \textless 0.05; **p \textless 0.01; ***p \textless 0.001.} \\ 

@@

  Afrosoricida & species & 23/42 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar3.pdf} & 1.75 & 1.08 \\ 
  Carnivora & family & 14/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar4.pdf} & 0.63 & 0.6 \\ 
  \textbf{Carnivora} & \textbf{genus} & \textbf{54/125} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar5.pdf} & \textbf{4.81**} & \textbf{1.78*} \\ 
  \textbf{Carnivora} & \textbf{species} & \textbf{76/283} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar6.pdf} & \textbf{7.66**} & \textbf{0.85} \\ 

@@

  Cetartiodactyla & genus & 100/128 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar8.pdf} & 0.85 & 0.94 \\ 
  \textbf{Cetartiodactyla} & \textbf{species} & \textbf{171/310} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar9.pdf} & \textbf{1.92*} & \textbf{-0.46} \\ 
  Chiroptera & family & 15/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar10.pdf} & -0.28 & 0.56 \\ 
  \textbf{Chiroptera} & \textbf{genus} & \textbf{93/202} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar11.pdf} & \textbf{13.47**} & \textbf{1.1} \\ 
  \textbf{Chiroptera} & \textbf{species} & \textbf{215/1053} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar12.pdf} & \textbf{8.82**} & \textbf{1.22} \\ 

@@

  Cingulata & genus & 8/9 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar14.pdf} & 1.51 & -1.57 \\ 
  \textbf{Cingulata} & \textbf{species} & \textbf{9/29} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar15.pdf} & \textbf{1.9*} & \textbf{0.11} \\ 

@@

  Dasyuromorphia & genus & 8/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar17.pdf} & -0.75 & -1.07 \\ 
  Dasyuromorphia & species & 9/64 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar18.pdf} & -0.88 & -0.34 \\ 

@@

  Didelphimorphia & species & 42/84 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar24.pdf} & -1.65 & 0.2 \\ 
  Diprotodontia & family & 11/11 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar25.pdf} &   &   \\ 
  Diprotodontia & genus & 25/38 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar26.pdf} & -1.13 & -1.31 \\ 
  Diprotodontia & species & 31/126 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar27.pdf} & 0.48 & -1.77 \\ 

@@

  Erinaceomorpha & species & 21/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar30.pdf} & -1.07 & -0.2 \\ 

@@

  Lagomorpha & family & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar34.pdf} &   &   \\ 
  Lagomorpha & genus & 5/12 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar35.pdf} & -1.06 & -0.95 \\ 
  Lagomorpha & species & 12/86 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar36.pdf} & -0.62 & -1.88 \\ 

@@

  Macroscelidea & species & 12/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar39.pdf} & -1.3 & -1.06 \\ 

@@

  Monotremata & genus & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar44.pdf} & -0.72 & -0.69 \\ 
  Monotremata & species & 2/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar45.pdf} & -0.97 & -0.97 \\ 

@@

  Paucituberculata & genus & 3/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar50.pdf} &   &   \\ 
  Paucituberculata & species & 5/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar51.pdf} &   &   \\ 

@@

  Peramelemorphia & species & 16/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar54.pdf} & -0.13 & 0.97 \\ 

@@

  Perissodactyla & species & 10/16 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar57.pdf} & -0.07 & -2.63 \\ 

@@

  Pholidota & species & 4/8 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar60.pdf} & 1.18 & 0.94 \\ 
  Pilosa & family & 4/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar61.pdf} & 1.87 & 2 \\ 
  Pilosa & genus & 4/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar62.pdf} & -0.96 & 0.36 \\ 
  \textbf{Pilosa} & \textbf{species} & \textbf{5/29} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar63.pdf} & \textbf{1.28} & \textbf{2.38*} \\ 

@@

  Primates & genus & 48/68 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar65.pdf} & -0.35 & -1.33 \\ 
  Primates & species & 64/351 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar66.pdf} & -0.67 & -1.27 \\ 

@@

  Proboscidea & genus & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar68.pdf} &   &   \\ 
  Proboscidea & species & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar69.pdf} & -0.69 & -0.69 \\ 
  Rodentia & family & 18/32 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar70.pdf} & 0.66 & -0.98 \\ 
  Rodentia & genus & 82/450 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar71.pdf} & -1.66 & 1.55 \\ 
  \textbf{Rodentia} & \textbf{species} & \textbf{90/2094} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar72.pdf} & \textbf{2.76*} & \textbf{2.34*} \\ 

@@

  Scandentia & genus & 2/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar74.pdf} & -0.74 & -0.74 \\ 
  Scandentia & species & 3/20 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar75.pdf} & -1.88 & -0.84 \\ 

@@

  Soricomorpha & family & 3/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar79.pdf} & -0.98 & -0.99 \\ 
  \textbf{Soricomorpha} & \textbf{genus} & \textbf{19/43} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar80.pdf} & \textbf{7.11**} & \textbf{2.59**} \\ 
  \textbf{Soricomorpha} & \textbf{species} & \textbf{21/392} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar81.pdf} & \textbf{10.65**} & \textbf{3.56**} \\ 
